### 2018-03-21 Writing/draft.tex
Comms + edits; going back to methods

\subsubsection{Character Difference ($CD$)}
\begin{equation}
    CD_{(x,y)} = 1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i} - y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right)
\end{equation}

\noindent Where $n$ is the number of taxa with comparable characters $x$, $y$ and $x_i$, $y_i$ are each characters states for the each $i^{th}$ taxon.
$CD$ is a continuous distance metric bounded between $0$ and $1$ (see the mathematical demonstration in the Supplementary Material 1).
Since we are considering differences as being only Fitch-like (non-additive) and unweighted, we calculated the difference between character states in a qualitative way.
Two same character states tokens have a difference of zero and two different ones have a difference of one (e.g. $0 - 0 = 0$ or $1 - 8 = 1$).
Additionally, we only consider differences for taxa with shared information \citep[i.e. a Gower distance;][]{GowerDist}.

We standardised each character by arbitrarily modifying their character state tokens (or symbols) by order of appearance.
In other words, we replaced all the occurrences of the first token to be $1$, the second to be $2$, etc.
%TG: Justification for the standardisation: basically, it makes comparisons faster and Fitch-like.
This procedure was used to treat all the characters are unordered with no assumption on the meaning of the character state (e.g. in a binary character $0$ is not necessary ancestral to $1$).
It also greatly improved the speed of our algorithm implementation to compare the characters.
This way, a character \texttt{A = \{2,2,3,0,0,3\}} for six taxa would be standardised as \texttt{A' = \{1,1,2,3,3,2\}} \citep[following the \textit{xyz} notation in][p.13]{felsenstein2004inferring}.
%MB: I don't get this part. What do you mean by standardized? And why are you doing this? Are you just editing the symbols?
Note that in terms of phylogenetic signal, both \texttt{A} and \texttt{A'} are exactly identical (forming three distinct groups).

@@

% Following these results, we encourage researchers to code characters that appear to be the most un-correlated \textit{a priori}.
% %MB: Do we? I'm not sure that I would. In practice, this would probably force morphologists to remove most of their characters.
% %MB: Making these kinds of recommendations leads to the risk that all you do is introduce biases into the dataset in another way.
% %TG: Fair enough, I'm happy to drop this whole paragraph.
% However, it is noteworthy to point that in rather small matrices, there was no significant difference in terms of recovering the right topology when maximising or randomising the character differences.
% %MB: How small? Be specific.
% Since many matrices are in this size range \citep{guillerme2016assessment} a simple bootstrap analysis (i.e. as an equivalent of randomising the character differences) can be sufficient to obtain good results (\textit{cf.} actively collecting different characters).

@@

\subsection{Limitations}
First, simulating evolutionary history is complex.
Not only because the models we're using to infer phylogenies are ever improving \citep[e.g.][]{heath2014fossilized,Wright01072016} but also because generalising morphological evolution across vastly different organisms is probably impossible.
This can lead to spuriously generated discrete morphological matrices
However, we do not compare the ``maximised'', ``minimised'' and ``randomised'' to the ``true'' tree but rather to the ``normal'' tree.
This allows us to reduce the caveats from our simulations on the effect of character correlation since we only compare the simulation end products to each other (the outputs) rather than to the simulation inputs.

@@

However, in modest size matrices (25 taxa; 100 to 350 characters), the effect of actively choosing to minimise character correlation was not more significant than simply bootstrapping the matrix, suggesting that character correlation is more a problem in large discrete morphological matrices.
For such matrices, minimising the character correlation (resampling characters $<25$\% different) or maximising it ($>75$\%) respectively significantly decreased and increased correct topological recovery compared to randomly resample matrices.
%MB: But at what point? How much correlation is needed to affect it? TG: added values.
%TG: do we want to suggest something here to close the conclusion? I agree we don't wanna be presecriptive Bristolians but it'll be nice to finsh with something like: "we're not saying it's a problem per se but maybe check your data?"

>>>>

\subsubsection{Character Difference ($CD$)}
\begin{equation}
    CD_{(x,y)} = 1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i} - y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right)
\end{equation}
%Why divide by 1/2 when you can just multiply by 2?

\noindent Where $n$ is the number of taxa with comparable characters $x$, $y$ and $x_i$, $y_i$ are each character's state for the $i^{th}$ taxon.
$CD$ is a continuous distance metric bounded between $0$ and $1$ (see the mathematical demonstration in the Supplementary Material 1).
Since we are considering differences as being only Fitch-like (non-additive) and unweighted, we calculated the difference between character states in a qualitative way.
Two same character states tokens have a difference of zero and two different ones have a difference of one (e.g. $0 - 0 = 0$ or $1 - 8 = 1$).
Additionally, we only consider differences for taxa with shared information \citep[i.e. a Gower distance;][]{GowerDist}.

We standardised each character by arbitrarily modifying their character state tokens (or symbols) by order of appearance.
In other words, we replaced all the occurrences of the first token to be $1$, the second to be $2$, etc.
%TG: Justification for the standardisation: basically, it makes comparisons faster and Fitch-like.
This procedure was used to treat all the characters are unordered with no assumption on the meaning of the character state (e.g. in a binary character $0$ is not necessary ancestral to $1$).
It also greatly improved the speed of our algorithm implementation to compare the characters.
This way, a character \texttt{A = \{2,2,3,0,0,3\}} for six taxa would be standardised as \texttt{A' = \{1,1,2,3,3,2\}} \citep[following the \textit{xyz} notation in][p.13]{felsenstein2004inferring}.
%MB: I don't get this part. What do you mean by standardized? And why are you doing this? Are you just editing the symbols?
Note that in terms of phylogenetic signal, both \texttt{A} and \texttt{A'} are exactly identical (forming three distinct groups).
%MB: Splits rather than groups, really. Since, in a rooted tree, at most one symbol will need to define a clade. All others could be plesiomorphic states.

@@

% Following these results, we encourage researchers to code characters that appear to be the most un-correlated \textit{a priori}.
% %MB: Do we? I'm not sure that I would. In practice, this would probably force morphologists to remove most of their characters.
% %MB: Making these kinds of recommendations leads to the risk that all you do is introduce biases into the dataset in another way.
% %TG: Fair enough, I'm happy to drop this whole paragraph.
% However, it is noteworthy to point that in rather small matrices, there was no significant difference in terms of recovering the right topology when maximising or randomising the character differences.
%MB: Agreed that that is noteworthy. I suspect I know why this happens (and you might have explained it earlier). It might actually be a statistical problem with our approach. When character similaritiy is maximized, how well resolved are the trees? 
% %MB: How small? Be specific.
% Since many matrices are in this size range \citep{guillerme2016assessment} a simple bootstrap analysis (i.e. as an equivalent of randomising the character differences) can be sufficient to obtain good results (\textit{cf.} actively collecting different characters).

@@

\subsection{Limitations}
%MB: I think what this section _really_ needs is an assessment of the method used to simulate correlations. It was basically accomplished by duplicating characters. It wasn't accomplished by evolving some characters with a particular covariance model (which probably would've been better). We kind of faked-up that model. 
First, simulating evolutionary history is complex.
Not only because the models we're using to infer phylogenies are ever improving \citep[e.g.][]{heath2014fossilized,Wright01072016} but also because generalising morphological evolution across vastly different organisms is probably impossible.
This can lead to spuriously generated discrete morphological matrices
However, we do not compare the ``maximised'', ``minimised'' and ``randomised'' to the ``true'' tree but rather to the ``normal'' tree.
This allows us to reduce the caveats from our simulations on the effect of character correlation since we only compare the simulation end products to each other (the outputs) rather than to the simulation inputs.

@@

However, in modest size matrices (25 taxa; 100 to 350 characters), the effect of actively choosing to minimise character correlation was not more significant than simply bootstrapping the matrix, suggesting that character correlation is more a problem in large discrete morphological matrices.
For such matrices, minimising the character correlation (resampling characters $<25$\% different) or maximising it ($>75$\%) respectively significantly decreased and increased correct topological recovery compared to randomly resample matrices.
%MB: But at what point? How much correlation is needed to affect it? TG: added values.
%TG: do we want to suggest something here to close the conclusion? I agree we don't wanna be presecriptive Bristolians but it'll be nice to finsh with something like: "we're not saying it's a problem per se but maybe check your data?"
%MB: Part of it is: we expect it to be a problem, but _when_ do we expect it to be a problem. There's the issue of "check your data", but it only raises the question: how? I think this is where we suggest avenues for future research (either here or move it up to the discussion). For instance, the simulations could be run in a way that more 'intelligently' places correlations in different parts of the tree. So, correlations are specifically modeled in an underlying stochastic process, for instance. We also don't really explore character congruence, that correlations can be ranked and spread over multiple internodes. We didn't look at ranking and we didn't look at competing correlations. There's a lot more that could be done here so, we might talk about that. Then we could talk about intelligent resampling measures, such as a targeted jackknifing that preferentially resamples characters that are highly similar to other characters etc.
